\chapter{LITERATURE REVIEW}\label{ch:literature-review}
\section{Introduction}\label{sec:introduction}
\justifying
Before discussing the study of ``Harnessing Artificial Intelligence for Enhanced
Learning Experiences in the Humanities'', it is imperative to first include a review of the most
important observations and viewpoints on the topic.
This chapter provides an overview of
the implementation or integration of AI in high education, focusing on practical ways of using AI-driven tools
to enhance academic performance and productivity.
Additionally,
this chapter addresses the challenges and opportunities associated with the use of AI in higher education
institutions in Morocco and abroad.
Finally, the chapter concludes with users' perceptions, which are consolidated with
statistics and studies conducted by researchers.
The aim is to clarify
what has been uncovered about this topic through the vivid opinions of users.

\section{Defining Key Concepts}\label{sec:defining-key-concepts}
\begin{itemize}
	\item \textbf{Artificial Intelligence (AI)}\label{AI} refers to the ability of a computer system to perform human
	tasks that can be accomplished by human Intelligence\citep{sadiku_ai_2021}.
%	2nd diff
	\item \textbf{AI-driven tools in education} encompass the application of AI tools like \say{ChatGPT} to assist 
	students, educators and administration in an education process.
	These AI-driven tools are used for planning and reactive execution of educational phases, such as
	student admission, lesson planning, knowledge delivery and performance evaluation\citep{mallik_proactive_2023}.
	Additionally, it serves as an extension of human intelligence, enabling
	increased productivity in the educational sphere by performing tasks
	such as problem-solving, learning, and decision-making\citep{cheng_widespread_2023}.
%	3rd diff
	\item \textbf{Learning experience in higher education}  refers to designing and implementing educational activities to create 
	positive and foster engaging student learning experiences \citep{kang_supporting_2023}.
	it involves comprehending and assessing the students’ educational experience, including 
	their satisfaction, self-efficacy, engagement, and self-regulated learning experience\citep{lyz_students_2022}.
	The focus is on improving the quality of education by enhancing students’ academic success, 
	readiness for self-education and self-development, and subject well-being \citep{iordache-platis_building_2018}.
% 4rd diff
	\item \textbf{Intelligent Tutoring Systems}
	are educational software that incorporates AI. The software monitors students' 
	progress, adjusts feedback, and provides hints to offer personalized 
	guidance \citep{shute_intelligent_2010}. Its aims to provide individualized, sophisticated instructional advice
	\citep{sedlmeier_intelligent_2001}.
	\item \textbf{ ChatBots }\label{chatbot} are computer programs that replicate human conversation with a conclusion. 
	While not all chatbots possess AI capabilities, modern chatbots are progressively 
	integrating AI techniques to analyze human input\citep{IBM_withnodate}.
	It enables the digitization of human interaction through written 
	or vocal means, giving the impression of ongoing communication with another individual \citep{oracle_what_nodate}.
	\item \textbf{Education Data Mining (EDM)}  is a technique that is used to evaluate students' academic performance, 
	assess the learning process, determine the overall quality of education, and enhance outcomes in higher education. 
	It entails processing and analyzing large amounts of data to extract relevant information that can be used for 
	decision-making and policy-making in the education sector \citep{arifin_using_2022}.
\end{itemize}

% the section
\section{The use of AI in Higher Education }\label{use-ai}
\justifying
Artificial intelligence has been increasingly integrated into various aspacts of higher
education, transforming traditional eduction \citep{wang_exploring_2023}. This section explores
some ways that AI can be used to enhance learning experiences and increas the academic studens' performance
by focusing on  personalized learning, intelligent tutoring, and administrative tasks automation.

\subsection{Personalized Learning}
The application of AI technology in higher education has been found to enhance academic performance and 
engagement by providing personalized learning experiences for students. By utilizing algorithms and 
data analysis, AI can recognize patterns in student performance and preferences, leading to personalized 
content and activity suggestions. This, in turn, enhances the student's learning experience, motivation, 
and engagement. Furthermore, AI can offer customized resources based on individual needs and learning styles 
while monitoring real-time progress to identify areas that require additional support and adjusting learning 
materials accordingly 
\citep{guerrero-quinonez_artificial_2023} and \citep{l_d_of_cs_akshara_first_grade_college_2023}.


% Personalized learning wih AI in higher education has the potential to enhance the academic peroformance and engagment
% by providing tailored learning experiences for students. Using AI technologies in education helps identifying patterns in student performance and preferences 
% through algorithms and data analysis. This enables personalized content and activity recommendations, enhancing the students' 
% learning experience, motivation, and engagement \citep{guerrero-quinonez_artificial_2023}. Also, it provides a tailored resources based on spacific 
% needs and learning styles. In addition, It can track and analysize progress in real-time, indetifying the gap areas that needs more support and adjusting the learining
% materials accordingly \citep{l_d_of_cs_akshara_first_grade_college_2023}.

\subsubsection{Intelligent Tutoring Systems (ITS) as module of Perosnalized learning}

Intelligent Tutoring Systems (ITS) have shown great promise in enhancing online learning 
through the use of AI. They provide personalized support, immediate feedback, and ongoing
monitoring for more effective and independent learning. By analyzing student data with
AI algorithms, these systems deliver tailored experiences that adapt to each student's needs,
offering relevant content and personalized feedback.
According to a recent study by \citep{l_d_of_cs_akshara_first_grade_college_2023}, it  improves 
adaptiveness and leverages personalized learning by taking into account the individual needs of each student. 
This approach to personalized learning is also supported by \citep{bradac_design_2022} who believe it can greatly 
improve students' learning experiences.

% Intelligent Tutoring Systems (ITS) offers a promising approach to enhance online learning
% with the help of AI, providing personalized support, instant feedback, 
% and continuous monitoring for more effective and autonomous learning. it uses AI algorithms anaylze students' data,
% enabling personalized experience. These systems are adaptative to the indiviual needs of students,
% offering relevent content and personalized feedback \citep{l_d_of_cs_akshara_first_grade_college_2023}. these
% systems improves the adaptiveness and laverage personalized learning by considering the individual needs of 
% each students \citep{bradac_design_2022}.
\subsection{ChatBots ``ChatGPT'' as a module}

ChatGPT has become a valuable tool in higher education, providing students with personalized 
recommendations based on their learning history. With minimal input, it can accurately answer 
questions and assist students in improving their study skills and time management. Additionally, 
it motivates and engages students by offering access to a vast array of resources. ChatGPT can even 
assess students' writing abilities \citep{mohammed_exploring_2023}. 
Moreover, ChatGPT serves as an effective teaching aid by enabling educators to make informed decisions 
and providing personalized support outside of regular class hours. It also promotes engagement and active 
learning through interactive and dynamic experiences, facilitating discussions, stimulating critical thinking, 
and delivering immediate feedback to enhance the learning experience \citep{schonberger_chatgpt_2023}. 
Ultimately, ChatGPT has the potential to enhance both learning and teaching processes, serving as an invaluable 
tool for class preparation, exam preparation, and personalized tutoring\citep{domenech_chatgpt_2023}. 

% old
% ChatGPT is a sophisticated AI-powered chatbot \footnote{ChatBots are computer programs that imitate human conversation. 
% They may not all have AI, but modern ones are using AI techniques to understand input. 
% ChatBots allow digital interaction to mimic real communication with humans.} powerd by \href{https://openai.com/}{Openai},
% has emerged as a valuable tool in the higher education landscape. It offers personalized 
% recommendation based on the students' learining history. In addition, ChatGPT can provide
% accurate answer to question with minimal input assisting students to improve their study skills
% and time managment and increase motivation and engagement with learning by providing access to a
% wide range of resources \citep{mohammed_exploring_2023}. ChatGPT can effectively shape
% teaching allowing educators to make the right decisions, providing personalized assitance and 
% support outside of regular class hours. it also prompt engagement and active learning
% roviding interactive and dynamic learning experiences. It can facilitate discussions, 
% prompt critical thinking, and offer immediate feedback, enhancing the overall learning process \citep{schonberger_chatgpt_2023}.
% ChatGPT has the potential to enhance learning and teaching processes, 
% providing benefits in class preparation, exam preparation, and as a personal tutor \citep{domenech_chatgpt_2023}.


\subsection{AI and Administrative Efficiency: Streamlining Operations}
Artificial intelligence has proven to be a valuable tool in enhancing administrative processes for educators. 
By automating tasks, educators can prioritize important activities such as curriculum design \citep{drach_use_2023}.
Furthermore, AI can streamline enrollment and improve retention rates, offering opportunities for resource optimization 
and successful online training experiences \citep{lukianets_promises_2023}. In addition, AI's data analysis capabilities 
and pedagogical reporting facilitate evidence-based decision-making, empowering educators to make informed choices\citep{guerrero-quinonez_artificial_2023}.

\subsubsection{Educational Data Mining (EDM) as a module}

Educational Data Mining (EDM) is a powerful tool for extracting knowledge from academic, socioeconomic, and 
learning analytics data. By utilizing statistical analysis, machine learning, and data mining techniques \citep{hooda_integrating_2022, arifin_using_2022},
EDM can significantly improve academic performance, learning quality, and decision-making. Recent studies have 
highlighted the effectiveness of EDM in predicting students' performance using practical techniques such as J48 \footnote{J48 is a decision tree algorithm that is commonly used in 
educational data mining (EDM) for classification tasks.} and K-means.\footnote{ K-means is a clustering algorithm that is often used in educational data mining 
(EDM) for grouping similar data points together. It is an unsupervised learning algorithm that aims to partition the data into K clusters, where K is a predefined number. 
The algorithm iteratively assigns data points to the nearest cluster centroid and updates the centroids until convergence. 
K-means is widely used in EDM for analyzing student behaviors and identifying patterns in educational data.}
With its potential to enhance overall efficiency and success\citep{prince_sattam_bin_abdulaziz_university_state_2016},
the use of Data Mining methods, particularly EDM, is becoming increasingly essential for educational institutions.

% old version
% EDM is a technique used to extract the knowledge from data and improve academic performance, learning quality, and decision-making. 
% It involves the use of statistical analysis, machine learning, and data mining to analyze academic, socioeconomic, 
% and learning analytics data \citep{hooda_integrating_2022, arifin_using_2022}. EDM has shown promising results in predicting students' 
% performance, with techniques like J48 \footnote{J48 is a decision tree algorithm that is commonly used in 
% educational data mining (EDM) for classification tasks.} and K-means \footnote{ K-means is a clustering algorithm that is often used in educational data mining 
% (EDM) for grouping similar data points together.  
% It is an unsupervised learning algorithm that aims to partition the data into K clusters, where K is a predefined number. 
% The algorithm iteratively assigns data points to the nearest cluster centroid and updates the centroids until convergence. 
% K-means is widely used in EDM for analyzing student behaviors and identifying patterns in educational data.} being effective \citep{prince_sattam_bin_abdulaziz_university_state_2016}. 
% The use of Data Mining methods in education, specifically EDM, has the potential to enhance the overall efficiency and success of educational institutions.

\section{Challenges of AI in higher education}
The emergence of artificial intelligence (AI) and its growing utilization in educational 
contexts have brought numerous challenges accompanying its implementation.  This section explores the obstacles 
and issues when integrating AI into education settings, particularly its use for academic purposes.
\subsection{AI bias}
Concerns have been raised regarding the potential negative impact of using AI in admission or grading processes for students. 
When AI algorithms are trained on biased data, they can produce racially biased output. For example, in medical appointment 
scheduling, certain algorithms predict that black patients are more likely to miss appointments compared to non-black patients. 
This perpetuates racial inequalities and creates a lack of access to healthcare, highlighting the crucial need for accuracy and 
fairness in AI. The implications of this extend beyond the medical field and into other domains 
such as education, judicial systems, and public safety \citep{shanklin_ethical_2022}. 
 Moreover, Yolder Himes suggests that biases in online exams can create barriers for students of different skin colors in STEM\footnote{science, technology, engineering and mathematics} 
fields.  The facial detection algorithms used by the software may be biased against students based on their skin tone or gender. The study shows 
that students with darker skin tones and black students are more likely to be marked for review, and women with darker skin tones are 
selected for review more often than white men. This highlights the need for caution when using automated proctoring software, as biased 
AI algorithms can have significant implications for education, social justice, equity, and diversity \citep{yoder-himes_racial_2022}. 

% In addition to that 
% Yolder Himes suggests that studenst of differenet skin color, face barriers in
% science, technology, engineering and mathematics(STEM) fields due to baises in online exam.
% The facial detection algorithms used by the software may be biased against students based on skin tones or gender.
% The study showed that students with darker skin tones and black students were more likely to be marked for review, 
% and women with the darkest skin tones were selected for review more often compared to the white men. Hence, 
% automated proctoring software may use biased AI algorithms, 
% which has implications for education, social justice, equity, and diversity \citep{yoder-himes_racial_2022}. 

\subsection{Data privacy}
